\section{Experience}

% IPsoft, Automation Manager, Europe
\cventry % chktex 1
  {\mbox{November 2018 -} \mbox{Present}}
  {Automation Team Manager, Europe}
  {IPsoft}{London}{}
  {
    Manager of the Automation team in Europe, responsible for the 
    development \& delivery of automations on the IPsoft IPcenter and 1Desk platforms.
    Development of client proof of concepts utilising a wide range of technologies and programming languages.
  }

% IPsoft, Automation Manager, United Kingdom
\cventry % chktex 1
  {\mbox{November 2016 -} \mbox{November 2018}}
  {Automation Team Lead, United Kingdom}
  {IPsoft}{London}{}
  {
    Regional lead of the Continual Service Improvement (automation) team responsible 
    for client automation development, architecture and API integrations. 
    Primarily focusing on automation targets for IPsoft banking clients. 
  }

% IPsoft, Senior Automation Engineer
\cventry % chktex 1
  {\mbox{June 2016 -} \mbox{November 2016}}
  {Senior Automation Engineer}
  {IPsoft}{London}{}
  {
    Development of high impact automations supporting software deployment, 
    application management and live reporting. In addition wrote and hosted 
    the automation training courses, with introductions to Python, JavaScript and PowerShell.
  }

% IPsoft, Automation Engineer
\cventry % chktex 1
  {\mbox{May 2015 -} \mbox{June 2016}}
  {Automation Engineer}
  {IPsoft}{London}{}
  {
    Event monitoring triggered Windows OS based automation development across 
    mutliple clients, with primary client requiring SC clearance.
  }

% Star Financial Systems, DevOps Engineer
\cventry % chktex 1
  {\mbox{May 2013 -} \mbox{May 2015}}
  {Development \& Operations Engineer}
  {Star Financial Systems}{London}{}
  {
    Responsible for the development of continuous deployment infrastructure 
    reducing time to production. Also owned the provising of production 
    instances the of Web trading platform developed by Star Financial Systems. 
  }

% GroupM, Senior Second Line Support Engineer
\cventry % chktex 1
  {\mbox{August 2012 -} \mbox{May 2013}}
  {Senior \nth{2} Line Support Engineer}
  {GroupM}{London}{}
  {
    Project work such as large scale OS provisioning/upgrades and software 
    deployment/remote configuration.
  }

% GroupM, Second Line Support Engineer
\cventry % chktex 1
  {\mbox{August 2009 -} \mbox{August 2012}}
  {\nth{2} Line Support Engineer}
  {GroupM}{London}{}
  {
    Hardware, OS and application support for staff across GroupM London offices.
  }

% British Army Reserves, F Company, 7 Battalion, The Rifles
\cventry % chktex 1
  {\mbox{May 2009 -} \mbox{July 2013}}
  {Rifleman}
  {British Army (Reserves), The Rifles Regiment}{London}{}
  {
    Infantry training improving team building and organizational skills through 
    monthly weekend and annual fortnight training courses.
  }

\closesection{}
