
\edef\hc{\string:}
% Cognizant, Associate Director
\cventry % chktex 1
  {\mbox{October 2023 -} \mbox{Present}}
  {Associate Director}
  {Cognizant}{London}{(Retail Banking Client)}
  {
    TBC
  }


% Contino, Senior Technical Principal
\cventry % chktex 1
  {\mbox{April 2022 -} \mbox{October 2023}}
  {Senior Technical Principal}
  {Contino}{London}{(Retail Banking Client)}
  {
    \textcolor{gray}{\textbf{Engineering Lead}}\\ 
    Cloud and automation-focused engineering lead across multiple workstreams 
    for a UK-based retail banking client. Provide support to engineering teams
    on client expectations, processes and technical requirements.
    Act as the final escalation point for all engineering decisions across 
    account workstreams. Coordinate client and supplier (Microsoft) teams on
    new engineering proposals as well as solving complex engineering problems.\\\\
    \textcolor{gray}{\textbf{Client Engagement}}\\ 
    Present technical overviews to senior stakeholders and introductory sessions
    to interested parties. Present and defend proposed designs at client 
    architecture governance forums.\\\\
    \textcolor{gray}{\textbf{Security \& Compliance}}\\ 
    Ensure that client compliance and regulatory controls are met from an engineering 
    perspective, and then appropriately evidenced to clients' satisfaction.
    Identify and document technology/process risks, then engage with various client
    security teams to agree mitigations.\\\\
    \textcolor{gray}{\textbf{Additional Responsibilities}}\\ 
    Additional responsibilities include supporting engineers with career
    progression (and upskilling), as well as performing technical interviews with
    with potential new hires.\\
  }

% Contino, Principal Consultant
\cventry % chktex 1
  {\mbox{September 2020 -} \mbox{April 2022}}
  {Principal Consultant}
  {Contino}{London}{(Retail Banking Client)}
  { 
    \textcolor{gray}{\textbf{Cloud Datacenter - Compute}}\\ 
    Design and build a compute pattern utilising Azure Virtual Machines, 
    supported with Azure Backup, Azure Automation, Azure Update Management,
    and Azure Policy to enforce the client's governance requirements.
    A heavy focus on security has required detailed investigation into 
    encryption options both at-rest and in-transit.\\\\
    \textcolor{gray}{\textbf{Cloud Datacenter - Storage}}\\ 
    Design and build the initial cloud datacenter landing zone based on
    a hub and spoke model. Designed and built a storage pattern utilising
    Azure File Storage, Azure Blob Storage and Azure Data Factory. This 
    feature was then evidenced with LLDs, ensuring it met the client's 
    governance controls.\\\\
    \textcolor{gray}{\textbf{Data Storage Assessment}}\\ 
    Assess the client's existing on-premise storage solution, perform
    an initial investigation of the type of data hosted, and then
    propose a suitable Azure based alternative. This report also took
    into account the ongoing classification of the data, along with 
    an initial migration strategy.\\\\
  }

% Contino, Senior Consultant
\cventry % chktex 1
  {\mbox{October 2019 -} \mbox{September 2020}}
  {Senior Consultant}
  {Contino}{London}{(Retail Banking Client)}
  {
    \textcolor{gray}{\textbf{Knowledge Transfer}}\\
    In addition training was provided
    to the client SRE team on platform maintenance and troubleshooting.\\\\
    \textcolor{gray}{\textbf{Cloud Control Framework}}\\
    Reviewed each of the controls in the clients cloud control framework, 
    agree on the evidence required for each of the controls. 
    Evidence was then generated to show that the controls were met for the 
    Cloud Native platform.\\\\
    \textcolor{gray}{\textbf{Cloud Native Platform}}\\
    Supported the engineering of a Cloud Native platform hosted in Azure. 
    This plafrom provided the client a plaform to develop Cloud Native applications
    hosted in Azure Kubernetes Clusters. A key focus on security required the implementation
    of Open Policy Agent, AquaSec and Istio Service Mesh.\\
  }

% IPsoft, Automation Manager, Europe
\cventry % chktex 1
  {\mbox{November 2018 -} \mbox{October 2019}}
  {Automation Team Manager, Europe}
  {IPsoft}{London}{(Retail Banking Client)}
  { 
    Manager of the Automation team in Europe, responsible for the 
    development \& delivery of automations on IPcenter: an IT service management 
    platform; as well as 1Desk: the next generation autonomic tool.\\~\\
    Led the project assigned by European CEO to containerise (Docker) our IPcenter 
    IT service management platform product using Kubernetes (Helm) within a 2-month timeframe. 
    The objectives achieved were to focus on the automation and related services, 
    producing a lightweight, rapidly deployable automation engine. 
    This product could be provisioned in AWS within minutes, including any client 
    customisation and pre-built automations. 
    Also included was an integration with Elastic Search to provide real-time 
    reporting of automation executions via Kibana dashboards.\\~\\
    Proposed and implemented the automation standardisation program to ensure all 
    automations conformed to the same documented development and testing standards. 
    This included the use of Python Sphinx / reStructuredText as well as the development 
    of automated QA reporting for automation engineers. 
    This has resulted in automations that are easily portable between instances, 
    as well as ensuring that engineers can support multiple clients effectively (without retraining).\\ 
  }

% IPsoft, Automation Manager, United Kingdom
\cventry % chktex 1
  {\mbox{November 2016 -} \mbox{November 2018}}
  {Automation Team Lead, United Kingdom}
  {IPsoft}{London}{(Retail Banking Client)}
  {
    Leading the automation team in the UK primarily working with our new client (a leading UK bank) to 
    configure the IPcenter AaaS Instance to their needs. This included developing custom 
    automations to execute on and remediate 10K+ Windows events from their monitoring platforms.\\~\\ 
    Also, I designed and implemented integrations with client CMDB data, password stores 
    and incident/change management (ServiceNow), using SQL and RESTful APIs. Since 
    implementation, the engineer time saved (as calculated by the client) has risen to approximately 
    10K hours per month.\\
  }

% IPsoft, Senior Automation Engineer
\cventry % chktex 1
  {\mbox{June 2016 -} \mbox{November 2016}}
  {Senior Automation Engineer}
  {IPsoft}{London}{(Media Agency Client)}
  {
    Client facing role writing requirements documents, then developing high impact automations. 
    Development is based on client requests as well as proactive suggestions based on experience 
    and analysis of event data using Jupyter.  All tasks were managed on JIRA sprint boards utilising 
    Bitbucket integration for git source control.\\~\\
    Automations primarily developed in JavaScript (backend) and Powershell, or Bash (client-side). 
    Where needed Python and Perl scripts were used to keep in line with client development frameworks.\\~\\
    Key automations:\\\\
    \textcolor{gray}{\textbf{SCOM agent reporting}}\\
    Query the SCOM APIs for agents in a downed state, on a schedule, 
    then rasing standard change requests via client systems, before restarting services on 
    the remote server. If required the agent would be upgraded. This would be followed up 
    with an HTML e-mail report to the product and server owners.\\\\
    \textcolor{gray}{\textbf{VM provision Web Form}}\\
    An automation that would generate a web form presenting options 
    to provision a VMware VM via PowerCli. Post-build scripts were deployed to VM to install 
    software requirements. This was written using JavaScript, HTML/CSS, PowerShell and Bash.\\\\
    \textcolor{gray}{\textbf{Pre-application deployment}}\\
    Multiple automations to stop application services across 
    multiple servers, before backing up config files (and databases), then calling external 
    deployments tools such as Jenkins. Finally restoring all services back to a running 
    state and validating their status.\\\\
    Wrote and hosted the automation training courses for internal and client staff. This included 
    training with the IPcenter platform as well as an introduction to JavaScript, PowerShell and Bash.\\
  }

% IPsoft, Automation Engineer
\cventry % chktex 1
  {\mbox{May 2015 -} \mbox{June 2016}}
  {Automation Engineer}
  {IPsoft}{London}{(Government Client)}
  {
    Developing automations to trigger on events generated from alerts monitored 
    by the IPcenter platform. 
    The automations developed were for Windows OS and application events, 
    remediation of the issues where performed where possible.\\~\\
  }

% Star Financial Systems, DevOps Engineer
\cventry % chktex 1
  {\mbox{May 2013 -} \mbox{May 2015}}
  {DevOps Engineer}
  {Star Financial Systems}{London}{(Internal)}
  {
    Build and maintenance of the VMware hosted QA environments, as well as the datacenter, 
    hosted production servers. Provisioning of the QA builds was achieved using PowerShell - PowerCli 
    on Windows Server 2008R2 with TeamCity for application build/unit testing and OctopusDeploy 
    for application deployment (and MSSQL backups).\\~\\
    The use of Octopus Deploy along with PowerShell scripting helped to reduce the deployment time 
    to production from more than 6-hours to 30-minutes (30+ services distributed over 5 or more Windows hosts).\\~\\
    The use of PowerCli allowed for on-demand provisioning of standardized testing host for development and QA teams. 
    This helped to ensure that all client production environments were closely replicated in QA/dev builds.\\~\\
    All tools were integrated with Slack APIs to ensure real-time notifications for all teams.
    Including alert notifications from Nagios monitoring for production client environments.\\
  }

